He-Man: A domain-specific language for lightweight concurrency

### 2011-12-13 report/report.tex
Finished Related Work.

The C10K problem is particularly evident in the context of HTTP servers, which
routinely maintain many concurrent connections. The popular Lighttpd and Nginx
HTTP server projects were both started with the explicit goal of addressing the
C10K problem \cite{Lighttpd,Nginx}, and both use event-based architectures
similar to He-Man.

A number of functional languages support lightweight threads with user-space
scheduling, most notably Erlang, which was designed for highly concurrent
telecommunications applications, and easily scales to 20,000 clients
\cite{Hellstrom}. Haskell

Haskell event loop stuff: \cite{LiZdancewic}

FoxNet: \cite{BiagioniEtAl}

As mentioned in the intro,
Haskell has epoll support and lightweight threads
Erlang

@@

\section{Evaluation}

>>>>

The C10K problem is particularly evident in the context of HTTP servers, which
routinely maintain many concurrent connections. As we discuss in Section
\ref{sec:evaluation}, Apache does not scale particularly well. The popular
Lighttpd and Nginx HTTP server projects were both started with the explicit goal
of outperforming Apache with respect to the C10K problem \cite{Lighttpd,Nginx},
and both use event-based architectures similar to He-Man.

A number of functional languages support lightweight threads with user-space
scheduling, most notably Erlang, which was designed for highly concurrent
telecommunications applications, and easily scales to 20,000 clients
\cite{Hellstrom}. The Haskell runtime supports a variety of concurrency
primitives which permit a lightweight threaded programming model \cite{LiEtAl}.

%A number of custom network stack implementations exist for functional
%languages, such as FoxNet for Standard ML \cite{BiagioniEtAl}, and

He-Man is most similar to Li and Zdancewic's Haskell implementation of a hybrid
event/thread programming model for network applications \cite{LiZdancewic}.
Their project has similar goals to ours, but is implemented entirely within
Haskell. As a result, unlike He-Man, the entire application must be written in
Haskell, and incurs runtime overhead from the Haskell system.

@@

\section{Evaluation}\label{sec:evaluation}
